Eagle: Making multiple-locus association mapping on a genome-wide scale routine

### 2018-07-22 AM+draft.tex
23/07 Discussion v1

Eagle is a new method (and R package) for multiple-locus association mapping. It differs from other multiple-locus methods. Its results are 
immediately interpretable,  it can handle much larger datasets due to dimension reduction, and it treats association mapping as a model selection instead of a variable selection problem which avoids multiple testing issues. As we saw in the simulation study, Eagle has considerably higher power than single-locus methods and is comparable in run time. However, the true worth of Eagle is apparent from the analyses of the mouse data. It  found 
more than double the SNP-trait associations than with single-locus association mapping, the method of choice. Furthermore, these extra results 
were not false positives but true verifiable results.  Eagle was built to make multiple-locus association mapping an attractive alternative 
to single-locus association mapping.

@@

>>>>

Eagle is a new method for multple-locus association mapping.

Eagle is a new method (and R package) for multiple-locus association mapping. It advances the state of multiple-locus association mapping 
in several ways. First, the results from Eagle are immediately interpretable. They are the set of SNPs in strongest association with the trait where 
each SNP identifies a separate genomic region of interest. Second, Eagle treats association mapping as a model selection instead of a 
variable selection problem. We do not have to content with thresholds and multiple testing issues.

 It differs from other multiple-locus methods. Its results are 
immediately interpretable,  it can handle much larger datasets due to dimension reduction, and it treats association mapping as a model selection instead of a variable selection problem avoiding threshold and  multiple testing issues. As we saw in the simulation study, Eagle has considerably higher power than single-locus methods but is comparable in run time. The true worth of Eagle is apparent from the analyses of the mouse data. It  found 
more than double the SNP-trait associations than with single-locus association mapping, the method of choice. Furthermore, these extra results 
were not false positives but true verifiable results.  Eagle was built to make multiple-locus association mapping an attractive alternative 
to single-locus association mapping.

@@

Over the past decade, GWASs have undergone great change. From their humble beginnings, GWASs are now widely accepted, having 
generated many new and reproducible discoveries.

What began as a fledgling and poorly understood platform

They have gone from a fledging, poorly understood
